Paper on the carbonate chemistry at Ny-Ålesund

### 2020-03-11 paper.Rmd
added paper.Rmd

---
title: "Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project" 
author: "Jean-Pierre Gattuso and Samir Alliouane"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  rmarkdown::html_document:
    theme: paper
    number_sections: false

---
![ ](Images/AWIPEV-Logo.jpg){width=250px}

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
library(tidyverse)
library(robfilter)
library(seacarb)
library(gridExtra)
library(reshape2)
library(lubridate)
library(lmtest)
library(grid)
library(viridis)
library(dygraphs)
require("knitr")
library("lmodel2")
library(captioner)
library(xts)
library(seismicRoll)
library(scales)
knitr::opts_chunk$set(echo = TRUE)

fig_nums <- captioner()
table_nums <- captioner(prefix = "Table")

@@

ggplotRegression <- function(fit){

require(ggplot2)

ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", se= FALSE) +
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5)))
}
```

>>>>

---
title: "Paper on the carbonate chemistry at Ny-Ålesund" 
author: "Jean-Pierre Gattuso, Samir Alliouane and Philipp Fischer"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  rmarkdown::html_document:
    theme: paper
    number_sections: false

---

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
library(tidyverse)
#library(robfilter)
library(seacarb)
library(gridExtra)
#library(reshape2)
library(lubridate)
#library(lmtest)
#library(grid)
library(viridis)
#library(dygraphs)
require("knitr")
library("lmodel2")
#library(captioner)
#library(xts)
#library(seismicRoll)
#library(scales)
knitr::opts_chunk$set(echo = TRUE)

#fig_nums <- captioner()
#table_nums <- captioner(prefix = "Table")

@@

ggplotRegression <- function(fit){
ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", se= FALSE) +
  labs(title = paste("Adj R2 = ", signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =", signif(fit$coef[[1]],5 ),
                     " Slope =", signif(fit$coef[[2]], 5),
                     " P =", signif(summary(fit)$coef[2,4], 5)))
}
```
